Cluster Dynamics with HETDEX at z < 0.5 - I: Simulated Performance, Mass Recovery, and Limits to Cosmology

### 2016-06-05 paper1.tex
redMaPPer formating

\subsection{Scale and Scatter of the Richness-Cluster Mass Relation}
Large-scale optical surveys (\eg, DES and LSST) expect to detect hundreds of thousands of galaxy clusters at $z < 1$. Because they produce photometry only, a major challenge for these surveys is relating a cluster observable to the total DM mass. One promising cluster mass estimator is the optical richness \citeeg{Abell1958}. Specifically, here, we use $\lambda$, the weighted number of galaxies within a scale aperture \citeeg{Rozo2011} as calculated by the redMapper algorithm \citep{Rykoff2012}. Previous works \citeeg{Rozo2010} show that the richness correlates strongly with cluster mass on the average, but the absolute mass scale of the optical richness mass estimator and the scatter in cluster mass at fixed optical richness are imprecisely known \citep{Rykoff2012}. These systematics remain the major source of uncertainty in deriving cosmological constraints from cluster abundances and must be measured using independent methods to realize the full potential of these types of surveys.

>>>>

\subsection{Scale and Scatter of the Richness-Cluster Mass Relation}
Large-scale optical surveys (\eg, DES and LSST) expect to detect hundreds of thousands of galaxy clusters at $z < 1$. Because they produce photometry only, a major challenge for these surveys is relating a cluster observable to the total DM mass. One promising cluster mass estimator is the optical richness \citeeg{Abell1958}. Specifically, here, we use $\lambda$, the weighted number of galaxies within a scale aperture \citeeg{Rozo2011} as calculated by the redMaPPer algorithm \citep{Rykoff2012}. Previous works \citeeg{Rozo2010} show that the richness correlates strongly with cluster mass on the average, but the absolute mass scale of the optical richness mass estimator and the scatter in cluster mass at fixed optical richness are imprecisely known \citep{Rykoff2012}. These systematics remain the major source of uncertainty in deriving cosmological constraints from cluster abundances and must be measured using independent methods to realize the full potential of these types of surveys.
